---
title: "InteractionExtension"
---

```{r}

# reproducible R environments
library(groundhog)

# dependencies
pkgs <- c(
  "dplyr",
  "ggplot2",
  "MASS", 
  "Matrix"
)

# activate libraries
suppressMessages(groundhog.library(pkgs, "2023-03-01"))
```



```{r}

# create a sample sheet
meta <- data.frame(
  sampleID = paste0("Sample", seq(1,9)),
  river = paste0("River", rep(seq(1,3), each = 3)),
  site = rep(paste0("Site", c(1,2,3)), 3)
)

meta$river_site <- paste(meta$rive, ":", meta$site, sep = "")
meta
```

Let's say there is a river-level correlation. This means:

  - There should be correlation between columns 1-3, 4-6, and 7-9.

Let's assume there is a site-level correlation. For instance, perhaps a level of a contaminant is high near the source and decays as you move further down the rive (up in site number). This means:

  - There should be a correlation between instances of `Site1`s, `Site2`s, and `Site3`s that is steadily decreasing.

```{r}
meta$river_site
```

```{r}

sigma <- matrix(
  c(
    0.5, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0,
    0.0, 0.5, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0,
    0.0, 0.0, 0.5, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0,
    0.0, 0.0, 0.0, 0.5, 0.0, 0.0, 0.0, 0.0, 0.0,
    0.0, 0.0, 0.0, 0.0, 0.5, 0.0, 0.0, 0.0, 0.0,
    0.0, 0.0, 0.0, 0.0, 0.0, 0.5, 0.0, 0.0, 0.0,
    0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.5, 0.0, 0.0,
    0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.5, 0.0,
    0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.5
  ), 9,9
) %>% t

sigma %>% data.frame()

(d <- Diagonal(n = 9, x = 0.5))
```


```{r}


complexCorMatrix <- function(meta, effect1, effect2)
{

  n <- ncol(meta)

  # effect1_levels <- unique(meta[, effect1])
  # effect2_levels <- unique(meta[, effect2])

  interactions <- paste(meta[, effect1$name], ":",
      meta[, effect2$name], sep = "")
  
  n <- length(interactions)
  
  df <- data.frame(matrix(0, nrow = n, ncol = n))

  rownames(df) <- interactions
  colnames(df) <- interactions

  # iterate through and add the cor conditionally
  for(i in 1:n){
    icol <- colnames(df)[i]
    for(j in 1:n){
      jcol <- rownames(df)[j]
    }
  }

}



complexCorMatrix(meta,
  list(name = "river", cor = 0.4),
  list(name = "site", cor = 0.2)
)

```













